On $R$-models

### 2019-04-22 PaperDraft.tex
updates in drafts and proofs

  Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale.
  The center of a quantale is the subquantale $\mathcal{Z}(\mathcal{Q}) = \{ a \in A \: | \: \forall b \in A, a \cdot b = b \cdot a \}$
\end{defin}

@@

>>>>

  Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale.
  The centre of a quantale is the subquantale $\mathcal{Z}(\mathcal{Q}) = \{ a \in A \: | \: \forall b \in A, a \cdot b = b \cdot a \}$
\end{defin}

@@

Following to Wurm, by the concept we mean a closed set of strings, that is, $A$ is a concept iff $A \triangleright
\triangleleft = A$. Moreover, $\langle \mathcal{B}_{\mathcal{L}}, \bigvee, \bigwedge \rangle$, where
$\mathcal{B}_{\mathcal{L}}$ is the set of $\triangleright \triangleleft$-closed subsets of $\mathcal{L}^{*}$.

We define a product of concepts as $A \circ B = (A \cdot B)^{\triangleright \triangleleft} =
\{ a b \: | \: a \in A, b \in B \}^{\triangleright \triangleleft}$.

Residuals are defined explicitly as follows:

\begin{center}
  $A \backslash B = \{ (a B, b) \: | \: (a, b) \in A^{\triangleright} \}^{\triangleleft}$

  $B / A = \{ (a, B b) \: | \: (a, b) \in A^{\triangleright} \}^{\triangleleft}$
\end{center}

It is easy to see, that the following condition hold for that residuals:

\begin{center}
  $A \backslash B = \{ C \: | \: A \circ C \leq B \}$

  $B / A = \bigvee \{ C \: | \: C \circ A \leq B \}$
\end{center}

\begin{defin}
  The syntax concept lattice of a language $L$ is a structure $\langle \mathcal{B}_{L}, \circ, \bigvee, \bigwedge, /,
  \backslash \rangle$, where $\mathcal{B}_{L}$ is the set of $[.]^{\triangleright \triangleleft}$-closed subsets of
  $\mathcal{L}^{*}$.
\end{defin}

\section{Thanks}

Author would like to thank Lev Beklemishev, Stepan Kuznetsov, Fedor Pakhomov, Danyar Shamkanov, and Andre Scedrov
for advice, critics, and comments.

### 2019-04-22 RModels.tex
updates in drafts and proofs

  \begin{enumerate}
    \item $\mathcal{M}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
    \item $\mathcal{M}, \langle a, b \rangle \Vdash A \bullet B \Leftrightarrow
      \text{there exists $c \in W$, $\mathcal{M}, a \Vdash A$ and $\mathcal{M}, b \Vdash B$}$;
    \item $\mathcal{M}, \langle a, b \rangle \Vdash A \backslash B \Leftrightarrow
      \text{for all $c \in R^{-1}(a)$, $\mathcal{M}, \langle c, a \rangle \Vdash A$ implies
      $\mathcal{M}, \langle c, b \rangle \Vdash B$}$;
    \item $\mathcal{M}, \langle a, b \rangle \Vdash B / A \Leftrightarrow
        \text{for all $c \in R(a)$, $\mathcal{M}, \langle a, c \rangle \Vdash A$ implies
        $\mathcal{M}, \langle b, c \rangle \Vdash B$}$;
    \item $\mathcal{M}, \langle a, b \rangle \Vdash \Gamma \rightarrow A \Leftrightarrow
    \mathcal{M}, \langle a, b \rangle \Vdash \Gamma \text{ implies } \mathcal{M}, \langle a, b \rangle \Vdash A$
  \end{enumerate}
\end{defin}

where $\mathcal{M}, \langle a, b \rangle \Vdash \Gamma$ denotes $\mathcal{M}, \langle a, b \rangle \Vdash A_1 \bullet \dots \bullet A_n$, or,
equivalently, there exist $c_1, \dots, c_{n-1}$,
such that $\mathcal{M}, \langle a, c_1 \rangle \Vdash A_1,
\mathcal{M}, \langle c_1, c_2 \rangle \Vdash A_2, \dots,
\mathcal{M}, \langle c_{n-1}, b \rangle \Vdash A_n$ implies that $\mathcal{M}, \langle a, b \rangle \Vdash B$.

@@

  \begin{enumerate}
    \item $f$ is onto;
    \item $\forall a, b \in W_1 (a R_1 b \Rightarrow f(a) R_2 f (b))$ (monotonicity);
    \item $\forall d \in W_1, c \in W_2, f(d) R_2 c \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: d R_1 c'$ (left lift property);
    \item $\forall d \in W_1, c \in W_2, c R_2 f(d) \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: c' R_1 d$ (right lift property);
  \end{enumerate}

@@

\begin{center}
 $\mathcal{M}_1, \langle a, b \rangle \Vdash p_i \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash p_i$
\end{center}

@@

\begin{lemma}
  Let $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$, then
  $\mathcal{M}_1, \langle a, b \rangle \Vdash A \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A$,
  for all $a, b \in W_1$ and for all $A \in Fm$
\end{lemma}

@@

  \begin{enumerate}
    \item $\Rightarrow$
      \begin{enumerate}
        \item Basic case: follows from the definition.
        \item Let $A \eqcirc B \bullet C$ and $\mathcal{M}_1, \langle a, b \rangle \Vdash B \bullet C$, then
        there exists $c \in W_1$, such that $\mathcal{M}_1, \langle a, c \rangle \Vdash B$ and
        $\mathcal{M}_1, \langle c, b \rangle \Vdash C$.

@@

        Thus, by IH, $\mathcal{M}_2, \langle f(a), f(c) \rangle \Vdash B$ and
        $\mathcal{M}_2, \langle f(c), f(b) \rangle \Vdash C$, so $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \bullet C$.
        \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_1, \langle a, b \rangle \Vdash B \backslash C$.
        Let $c \in W_2$, such that $c R_2 f(a)$.

@@

        Thus, $\mathcal{M}_1, \langle d, a \rangle \Vdash A$ implies
        $\mathcal{M}_1, \langle d, b \rangle \Vdash B$.

        By IH, $\mathcal{M}_2, \langle c, f(a) \rangle \Vdash A$ implies
        $\mathcal{M}_2, \langle c, f(b) \rangle \Vdash B$, then $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A \backslash B$.

@@

      \item Let $A \eqcirc B \bullet C$.
      Let $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \bullet C$. Then
      there exists $c \in W_2$, such that $\mathcal{M}_2, \langle f(a), c \rangle \Vdash B$ and
      $\mathcal{M}_2, \langle c, f(b) \rangle \Vdash C$.

      So far as $f$ is surjection, then there exists $d \in W_1$, such that
      $c = f(d)$, then $\mathcal{M}_2, \langle f(a), f(d) \rangle \Vdash B$ and
      $\mathcal{M}_2, \langle f(d), f(b) \rangle \Vdash C$, and, by IH,
      $\mathcal{M}_1, \langle a, d \rangle \Vdash B$ and $\mathcal{M}_1, \langle d, b \rangle \Vdash C$,
      then $\mathcal{M}_1, \langle a, b \rangle \Vdash B \bullet C$.

      \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \backslash C$.

      Let $c \in W_1$ and $c R_1 a$, then $f(c) R_1 f(a)$ by monotonicity,
      so $\mathcal{M}_2, \langle f(c), f(a) \rangle \Vdash A$ implies
      $\mathcal{M}_2, \langle f(c), f(b) \rangle \Vdash B$.

      By IH, $\mathcal{M}_1, \langle c, a \rangle \Vdash A$ implies
      $\mathcal{M}_1, \langle c, b \rangle \Vdash B$. Thus, $\mathcal{M}_1, \langle c, a \rangle \Vdash A \backslash B$.
      \item Similarly to (c).
    \end{enumerate}
  \end{enumerate}
\end{proof}

@@

    Then $\mathcal{M}_1, \langle a, b \rangle \Vdash A$, thus $\mathcal{M}_2 \langle f(a), f(b) \rangle \Vdash A$.
    That is, $\mathcal{M}_2 \langle c, d \rangle \Vdash A$

@@

  Let $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$ and $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$, such that
  for all $p \in Tp$,
  $\mathcal{M}_1, \langle a, b \rangle \Vdash p \Leftrightarrow_{def} \mathcal{M}_1, \langle f(a), f(b) \rangle \Vdash p$.
  Thus, $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$ and $\mathcal{M}_1 \models A$. Thus, $\mathcal{M}_2 \models A$.
\end{enumerate}
\end{proof}

>>>>

  \begin{enumerate}
    \item $\mathcal{M}, w \models p_i \Leftrightarrow w \in v(p_i)$;
    \item $\mathcal{M}, \langle a, b \rangle \models A \bullet B \Leftrightarrow
      \text{there exists $c \in W$, $\mathcal{M}, a \models A$ and $\mathcal{M}, b \models B$}$;
    \item $\mathcal{M}, \langle a, b \rangle \models A \backslash B \Leftrightarrow
      \text{for all $c \in R^{-1}(a)$, $\mathcal{M}, \langle c, a \rangle \models A$ implies
      $\mathcal{M}, \langle c, b \rangle \models B$}$;
    \item $\mathcal{M}, \langle a, b \rangle \models B / A \Leftrightarrow
        \text{for all $c \in R(a)$, $\mathcal{M}, \langle a, c \rangle \models A$ implies
        $\mathcal{M}, \langle b, c \rangle \models B$}$;
    \item $\mathcal{M}, \langle a, b \rangle \models \Gamma \rightarrow A \Leftrightarrow
    \mathcal{M}, \langle a, b \rangle \models \Gamma \text{ implies } \mathcal{M}, \langle a, b \rangle \models A$
  \end{enumerate}
\end{defin}

where $\mathcal{M}, \langle a, b \rangle \models \Gamma$ denotes $\mathcal{M}, \langle a, b \rangle \models A_1 \bullet \dots \bullet A_n$, or,
equivalently, there exist $c_1, \dots, c_{n-1}$, such that $\mathcal{M}, \langle a, c_1 \rangle \models A_1,
\mathcal{M}, \langle c_1, c_2 \rangle \models A_2, \dots, \mathcal{M}, \langle c_{n-1}, b \rangle \models A_n$ implies that
$\mathcal{M}, \langle a, b \rangle \models B$.

@@

  \begin{enumerate}
    \item $f$ is onto;
    \item $\forall a, b \in W_1 (a R_1 b \Rightarrow f(a) R_2 f (b))$ (monotonicity);
    \item $\forall d \in W_1, c \in W_2, f(d) R_2 c \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: d R_1 c'$ (left lift property);
    \item $\forall d \in W_1, c \in W_2, c R_2 f(d) \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: c' R_1 d$ (right lift property).
  \end{enumerate}

@@

\begin{center}
 $\mathcal{M}_1, \langle a, b \rangle \models p_i \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \models p_i$
\end{center}

@@

\begin{lemma}
  Let $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$, then
  $\mathcal{M}_1, \langle a, b \rangle \models A \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \models A$,
  for all $a, b \in W_1$ and for all $A \in Fm$
\end{lemma}

@@

  \begin{enumerate}
    \item $\Rightarrow$
      \begin{enumerate}
        \item Basic case: follows from the definition.
        \item Let $A \eqcirc B \bullet C$ and $\mathcal{M}_1, \langle a, b \rangle \models B \bullet C$, then
        there exists $c \in W_1$, such that $\mathcal{M}_1, \langle a, c \rangle \models B$ and
        $\mathcal{M}_1, \langle c, b \rangle \models C$.

@@

        Thus, by IH, $\mathcal{M}_2, \langle f(a), f(c) \rangle \models B$ and
        $\mathcal{M}_2, \langle f(c), f(b) \rangle \models C$, so $\mathcal{M}_2, \langle f(a), f(b) \rangle \models B \bullet C$.
        \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_1, \langle a, b \rangle \models B \backslash C$.
        Let $c \in W_2$, such that $c R_2 f(a)$.

@@

        Thus, $\mathcal{M}_1, \langle d, a \rangle \models A$ implies
        $\mathcal{M}_1, \langle d, b \rangle \models B$.

        By IH, $\mathcal{M}_2, \langle c, f(a) \rangle \models A$ implies
        $\mathcal{M}_2, \langle c, f(b) \rangle \models B$, then $\mathcal{M}_2, \langle f(a), f(b) \rangle \models A \backslash B$.

@@

      \item Let $A \eqcirc B \bullet C$.
      Let $\mathcal{M}_2, \langle f(a), f(b) \rangle \models B \bullet C$. Then
      there exists $c \in W_2$, such that $\mathcal{M}_2, \langle f(a), c \rangle \models B$ and
      $\mathcal{M}_2, \langle c, f(b) \rangle \models C$.

      So far as $f$ is onto, then there exists $d \in W_1$, such that $c = f(d)$, then $\mathcal{M}_2, \langle f(a), f(d) \rangle \models B$ and
      $\mathcal{M}_2, \langle f(d), f(b) \rangle \models C$, and, by IH, $\mathcal{M}_1, \langle a, d \rangle \models B$ and
      $\mathcal{M}_1, \langle d, b \rangle \models C$, then $\mathcal{M}_1, \langle a, b \rangle \models B \bullet C$.

      \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_2, \langle f(a), f(b) \rangle \models B \backslash C$.

      Let $c \in W_1$ and $c R_1 a$, then $f(c) R_1 f(a)$ by monotonicity, so $\mathcal{M}_2, \langle f(c), f(a) \rangle \models A$ implies
      $\mathcal{M}_2, \langle f(c), f(b) \rangle \models B$.

      By IH, $\mathcal{M}_1, \langle c, a \rangle \models A$ implies $\mathcal{M}_1, \langle c, b \rangle \models B$. Thus,
      $\mathcal{M}_1, \langle c, a \rangle \models A \backslash B$.
      \item Similarly to (c).
    \end{enumerate}
  \end{enumerate}
\end{proof}

@@

    Then $\mathcal{M}_1, \langle a, b \rangle \models A$, thus $\mathcal{M}_2 \langle f(a), f(b) \rangle \models A$.
    That is, $\mathcal{M}_2 \langle c, d \rangle \models A$

@@

  Let $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$ and $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$, such that
  for all $p \in Tp$, $\mathcal{M}_1, \langle a, b \rangle \models p \Leftrightarrow_{def} \mathcal{M}_1, \langle f(a), f(b) \rangle \models p$.
  Thus, $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$ and $\mathcal{M}_1 \models A$. Thus, $\mathcal{M}_2 \models A$.
\end{enumerate}
\end{proof}

\begin{enumerate}
  \item Let $\mathcal{F} = \langle W, R \rangle$ be a transitive frame and $V \subseteq W$, such that $V \neq \emptyset$ and $V$ is
  downward and upward closed with respect to $R$. Then a frame $\mathcal{F} \restriction V = \langle V, R \cap V \times V \rangle$ is a generated subframe.
  \item If, $\mathcal{M} = \langle W, R, \theta$ and $V \subseteq W$, such that $\mathcal{F} \restriction V$ is a genereted subframe. Then
  $\mathcal{M} \restriction V = \langle V, R \cap V \times V, \theta^{'}\rangle$ is a generated submodel, where $\theta^{'}(p) = \theta(p) \cap V$.
\end{enumerate}
\end{defin}

\begin{lemma}
  Let $\mathcal{M} = \langle W, R, \theta$ and $V$ is $R$-closed subset of $W$, then:
  \begin{enumerate}
    \item If $a, b \in V$, then $\mathcal{M}, \langle a, b \rangle \models A$ iff $\mathcal{M} \restriction V, \langle a, b \rangle \models A$;
    \item $Log(\mathcal{F}) \subseteq Log(\mathcal{F} \restriction V)$
  \end{enumerate}
\end{lemma}

\begin{proof}
  $ $
  \begin{enumerate}
    \item
    \begin{enumerate}
      \item Let $a, b \in V$ and $\langle a, b \rangle \in \theta(p)$, then $\mathcal{M} \restriction V, \langle a, b \rangle \models p$, for $p \in Tp$.
      \item Let $A \eqcirc B \bullet C$ and $\mathcal{M}, \langle a, b \rangle \models B \bullet C$, then
      there exists $c \in W$, such that $a R C$ and $\mathcal{M}, \langle a, c \rangle \models B$, $c R b$ and $\mathcal{M}, \langle c, b \rangle \models C$.
      So far as $V$ is upwardly and downwardly closed, then $c \in V$. Then, by IH, $\mathcal{M} \restriction V , \langle a, c \rangle \models B$, $c R b$ and
      $\mathcal{M} \restriction V, \langle c, b \rangle \models C$. So $\mathcal{M} \restriction V \langle a, b \rangle \models B \bullet C$.
      \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}, \langle a, b \rangle \models B \backslash C$. Then for all $c \in R^{-1}(a)$, $\mathcal{M},
      \langle c, a \rangle \models B$ implies $\mathcal{M}, \langle c, b \rangle \models C$. Let $\mathcal{M}, \langle c, a \rangle \models B$.
      By IH, $\mathcal{M} \restriction V, \langle c, a \rangle \models B$.

      $c \in V$, because $V$ is $R$-closed upwardly and downloadly. On the other hand, $c R b$, so $b \in V$. Hence,
      $\langle c, b \rangle \in \mathcal{F} \restriction V$. By IH, $\mathcal{M} \restriction V, \langle c, b \rangle \models C$. Hence,
      $\mathcal{M} \restriction V, \langle a, b \rangle \models A \backslash B$.
    \end{enumerate}
    \item Let $\mathcal{F} \restriction V\not\models \Gamma \to A$. Then there exist a valuation $v$ and $\langle a, b \rangle \in R \cap V \times V$,
    such that $\mathcal{M} \restriction V, \langle a,b \rangle \models \Gamma$ and $\mathcal{M} \restriction V, \langle a,b \rangle\not\models A$.

    Let us define a valuation $v^{'}$ for the frame $\mathcal{F}$, such that $v(p) = v^{'}(p)$. Then, by the first part, $\mathcal{M}, \langle a, b \rangle \models \Gamma$ and $\mathcal{M}, \langle a, b\rangle\not\models A$. So, $\mathcal{F}\not\models \Gamma \to A$.
  \end{enumerate}
\end{proof}

\begin{col}
  $ $

  Let $\mathcal{F}$ be a frame and $\mathcal{F} \restriction V$ is a generated subframe of $\mathcal{F}$.
  Then $Log(\mathcal{F}) = Log(\mathcal{F} \restriction V)$.
\end{col}

Let $\mathbb{Z}^{*}$ be the set of all finite sequences of integers. Let us define the following relation $R$.
